Stable Hot Spot Analysis (Draft)

### 2017-06-16 paper-main.tex
Added Appendix

\subsection{Clumping}

@@

The aggregation level is a slice plane through our three dimensional space. 
We evalute only the aggregation with fixed W and fixed F.
\begin{definition} Aggregation run:
\begin{displaymath}
\SOHUP( G^*(R_z, W, st, F), G^*(R_{z+1}, W, st, F) )
\end{displaymath}
\begin{displaymath}
\SOHDOWN( G^*(R_z, W, st, F), G^*(R_{z+1}, W, st, F) )
\end{displaymath}
\begin{displaymath}
z \in [1,6], dim(W)=11,dim(F)=41, G^* \in [Standard, Focal]
\end{displaymath}
\end{definition}

The results can be found in figure ~\ref{fig:Zoom}.
For the upward property, $G^*$ is always better than Focal $G^*$, compared to the results from figure
\ref{fig:SoHZoom}. Focal $G^*$ reaches the same result as $G^*$ at zoom level 5 .
For the downward property, Focal $G^*$ leads to better results at zoom level 5.

@@

\subsection{Blur}

Blur is a slice plane through our three dimensional space. 
W is changed from 7 to 29 with a stepsize of 2, F and the aggregation level is fixed.
\begin{definition} Blur run:
\begin{displaymath}
\SOHUP( G^*(R_z, W_i, st, F), G^*(R_{z}, W_{i+1}, st, F) )
\end{displaymath}
\begin{displaymath}
\SOHDOWN( G^*(R_z, W_i, st, F), G^*(R_{z}, W_{i+1}, st, F) )
\end{displaymath}
\begin{displaymath}
z =3, i \in [1,6],dim(F)=41, G^* \in [Standard, Focal]
\end{displaymath}
\end{definition}
The blur results are plotted in Fig.~\ref{fig:Blur}.
The slice plane of the weight dimension is consistent with figure ~\ref{fig:SoHWeight}.
Higher weight leads in general to better results for Focal $G^*$. 
$G^*$ doesn't fit to the mean of our whiskerplot.

@@

  \caption{
    Example clustering for G* and Focal G* used as a input for SoH computation.
  }
\end{figure*}

>>>>

\section{Appendix}

\subsection{Clumping}
The SoH needs a parent and a child. Clusters can be calculated different. For $G^*$ a sigmoid can be used. Values above 2.58 and under -2.58 means in less then 
1\% of the cases you are wrong. The values of Focal $G^*$ depend on the focal size F. Therefore, we decide all values in the top quantile belong to a clusters.
For clustering we grouped the neighbourhood with values in the top quantile to one cluster. 
Neigbours are defined if they can be reached with a stepsize of 1 in x and y direction, independent of each other.
Which can be expressed in R with clumping, TODO which package and parametrisations.
In Fig.~\ref{fig:Clumping} we visualized the clusters. The clusters are marked in different colours yellow (child) and violet (parent).
It can seen that the results from $G^*$ and Focal $G^*$ differ. Focal $G^*$ has more smaller clusters which are distributed over the complete raster.
Not overlapping clusters should be not stable because if we changed the parametrisation we want that the clusters do not disappear or appear. 
The SoH defines in more detail, which changes for the clusters are stable and which changes indicate that the clusters are instable.

  \caption{
    Example clustering for G* and Focal G* used as a input for SoH computation.
  }
  \label{fig:Clumping}
\end{figure*}

@@

The aggregation level is a slice plane through our three dimensional space. 
This is an example how the results can look with visualize representations of the calculated 
rasters and the raw data.
We evalute only the aggregation with fixed W and fixed F.
\begin{definition} Aggregation run:
\begin{displaymath}
\SOHUP( G^*(R_z, W, st, F), G^*(R_{z+1}, W, st, F) )
\end{displaymath}
\begin{displaymath}
\SOHDOWN( G^*(R_z, W, st, F), G^*(R_{z+1}, W, st, F) )
\end{displaymath}
\begin{displaymath}
z \in [1,6], dim(W)=11,dim(F)=41, G^* \in [Standard, Focal]
\end{displaymath}
\end{definition}

The results can be found in figure ~\ref{fig:Zoom}. It can be seen that with an increase of the aggregation level the values 
increase. TODO if clusters increase/decrease
For the upward property, $G^*$ is always better than Focal $G^*$, compared to the results from figure
\ref{fig:SoHZoom}. Focal $G^*$ reaches the same result as $G^*$ at zoom level 5 .
For the downward property, Focal $G^*$ leads to better results at zoom level 5.

@@

\subsection{Blur}
We also made an example for the variation of the weight size.
Blur is a slice plane through our three dimensional space. 
W is changed from 7 to 29 with a stepsize of 2, F and the aggregation level is fixed.
\begin{definition} Blur run:
\begin{displaymath}
\SOHUP( G^*(R_z, W_i, st, F), G^*(R_{z}, W_{i+2}, st, F) )
\end{displaymath}
\begin{displaymath}
\SOHDOWN( G^*(R_z, W_i, st, F), G^*(R_{z}, W_{i+2}, st, F) )
\end{displaymath}
\begin{displaymath}
z =3, i \in [1,6],dim(F)=41, G^* \in [Standard, Focal]
\end{displaymath}
\end{definition}
The blur results are plotted in Fig.~\ref{fig:Blur}. We show how the weight matrix is increasing
and how $G^*$ and Focal $G^*$ changes bases on W.
The slice plane of the weight dimension is consistent with figure ~\ref{fig:SoHWeight}.
Higher weight leads in general to better results for Focal $G^*$. 
$G^*$ doesn't fit to the mean of our whiskerplot.

@@
